A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-01-21 paper/paper.tex
more definitions about nu-sets and making explicit the link with parametricity

\subsection{Generalization to \texorpdfstring{$\nu$}{ν}-sets}
Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets. To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner by taking sequences of elements of a set $\nu$ of arbitrary cardinal, extended with $\kstar$. That is:

@@

>>>>

\subsection{Generalization to \texorpdfstring{$\nu$}{ν}-sets}
Let us call $\nu$-sets, the generalization of augmented semi-simplicial sets and semi-cubical sets. To obtain this, we extend $\DeltaPlus$ and $\Cube$ in a straightforward manner into a category which we call $\nu$-semi-shape category. The morphisms of the $\nu$-semi-shape category are sequences of elements of a set $\nu$ of arbitrary cardinal, extended with $\kstar$, so that the following holds:

@@

A $\nu$-set is thus a functor $\phi$ from the $\nu$-semi-shape category to $\Set$ and we call $n$-$\nu$-semi-shape an element of $\phi(n)$. As in the augmented semi-simplicial and semi-cubical cases, the standard $(n+1)$-$\nu$-semi-shape is obtained by connecting together $\nu$ copies of the standard $n$-$\nu$-semi-shape with an extra copy stretched in a new dimension. We clarify in the next sections how this process of construction is similar to the parametricity translation considered in the context of typed programming languages~\cite{reynolds72, bernardy10, bernardy11, atkey14, bernardy15}.
